---
title: "p8105_hw1_sl5454"
output: html_document
date: "2024-09-12"
---

```{r}
library(tidyverse)
```

##Problem 1

```{r problem_1}
data("penguins", package = "palmerpenguins")

num_row = nrow(penguins)
num_col = ncol(penguins)
mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)
summary(penguins)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")

ggsave("flipper_vs_bill_scatterplot.pdf")
```
The penguins data set contains observations of three species of penguins collected from three islands.The data set includes sex, years, and various physical measurements of the 
penguins, such as flipper length, which has an average value of 200.9152.The dataset consists of 344 #rows and 8 columns, but some measurements contain missing data.

##Problem 2

```{r}
p2_df =
  tibble(
    sample = rnorm(n = 10),
    log_samp = sample > 0,
    char_vector = sample(letters, 10, replace = TRUE),
    f_vector = factor(sample(c("level1", "level2", "level3"), 10, replace = TRUE))
  )

sample_vec = pull(p2_df, sample)
mean_samp = mean(sample_vec)

log_samp_vec = pull(p2_df, log_samp)
mean_log = mean(log_samp_vec)

char_vec = pull(p2_df, char_vector)
mean_char = mean(char_vec)

f_vec = pull(p2_df, f_vector)
mean_fact = mean(f_vec)
```

The mean of a random sample and a logical vector can be calculated because they are numerical vectors.
The mean of a character vector and a factor vector with 3 different factor “levels” can't be calculated because they are character vectors.

```{r, echo = TRUE, results = hide}
num_log = as.numeric(p2_df[["log_samp"]])
num_char = as.numeric(p2_df[["char_vector"]])
num_f = as.numeric(p2_df[["f_vector"]])
```

The "as.numeric" function converts logical values to numbers as below:
"TRUE" becomes "1", and "FALSE" becomes "0"
This conversion works because logical values are binary. The means can be calulated after the conversion and the result represents the proportion of "TRUE" in the vector.

The "as.numeric" function converts character vectors to "NA" because a character can't be represented by numbers. Thus, calculating the mean of character vectors will fail or produce "NA".

The "as.numeric" function converts levels of factor vectors to corresponding numbers as follows:
"level 1" becomes "1"
"level 2" becomes "2"
"level 3" becomes "3"
This conversion works because different levels can indicated by numbers. However, these numbers don't have the meanings as factor levels do. Thus, the means of factor vectors is not meaningful.

